Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-06-03 glsb.tex
working on discussion

\section{TO DO}
\begin{itemize}
\item{plug in numbers from Lauren's metallicity gradients}
  \item{expand discussion of Kasperova14}
\end{itemize}

@@

We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, in line with the previous results for Malin 1 \citep{Barth07} and NGC 7589 \citep{Lelli10}.

@@

It also seems unlikely that GLSBs are just extreme versions of normal disk galaxies \citep{Das13}.  It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.

Accretion can also form GLSB systems around any type of host galaxy, explaining how \citet{Barth07} can find that Malin~1 is an SB0 galaxy, while our two systems are normal ellipticals.

%Our initial long slit observations don't really show much as far as correlation between the bulge and disk rotation vectors.  We are currently proposing for higher resolution observations that will make it possible to measure the stellar kinematics of the central object in detail to see if it is a relatively undisturbed elliptical.

@@

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).  For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.  This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.  \citet{MacArthur04} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.  Using braidband colors, \citet{MacArthur04} also found metallicity gradients of $\sim0$\ to $-0.1$ dex kpc$^{-1}$, at least a factor of two less than what we observe in Malin~2. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.

While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.  Since modern photometric surveys are often surface brightness limited, it is possible a gLSB system will be found in the future that is the decendent of a collisional ring system.

@@

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs.
%Thanks to the observing specialists at Apache Point for their help executing our remote observations.

>>>>

@@

We find that the centers of these two GLSB systems very closely resemble normal galaxies, with the extended faint disks being distinct components, consistent with the previous results for Malin~1 \citep{Barth07} and NGC~7589 \citep{Lelli10}.

@@

It also seems unlikely that GLSBs are just extreme versions of normal disk galaxies \citep{Das13}.  It's hard to imagine how such a large massive central spheroid could be formed without also disrupting the surrounding disk.  While the old stellar populations in the disks of Malin~2 and UGC~6614 are evidence against the \citet{Mapelli08} formation scenario, we have not addressed what collisional ring galaxies do evolve into.  Since photometric surveys are often surface brightness limited, it is possible a GLSB system will be found in the future that is the decendent of a collisional ring system.

One of the most important features we can see in our data is the sharp metallicity gradient as one transitions between the central region and the disk in both Malin~2 and UGC~6614 (Figures~\ref{metal_malin2} and~\ref{metal_ugc}).  For both galaxies, the best fitting star formation histories show the stellar populations are dominated by old stars inside and outside the transition, but the metallicity changes by $\sim0.7-1.0$ dex.  This is a very sharp gradient compared to what has been found in normal spirals for the bulge-to-disk transition region.  \citet{MacArthur09} spectroscopically observed a range of spiral galaxies and found the metallicity profiles which were dropping, rising, and flat.  Using broadband colors, \citet{MacArthur04} also found metallicity gradients were generally very shallow, with steep metallicity gradients only in very late-type spiral galaxies. Also note that our metallicity gradient could be an underestimate of the true gradient since the central metallicities are at the limits of our model grid, and we have spatially binned data, possibly washing out how sharp the transition is.

\citet{Kasparova14} present one of the most in depth observational studies of Malin~2.  Mass-modeling the system, they find that a huge isothermal core with $r_c=27.3$ kpc.  \citet{Kasparova14} also measure gas metallicities and find the metallicity drops from solar in the center of the system to half-solar at $r=30$\ kpc.  It is probably foolish to directly compare gas and stellar metallicities, but it is interesting that the gas metallicity gradient appears to be much lower than the stellar gradient.  This is probably consistent with a low metallicity gas-rich galaxy merging with an elliptical system that has much higher stellar metallicity, although a detailed simulation would be heklpful in confirming what the final expected gas metallicity gradient should be.

@@

@@

%--------------------------------------
\acknowledgments
Thanks to Dave Doss and the staff at McDonald Observatory for their help on these observing runs. Thanks to Dmitry Bizyaev for stimulating conversations about gLSBs. Thanks to Lauren MacArthur for discussions on stellar metallicity gradients.
%Thanks to the observing specialists at Apache Point for their help executing our remote observations.
